# Introduction {#intro}


By default, bookdown merges all Rmd files by the order of filenames, e.g., `01-intro.Rmd` will appear before `02-literature.Rmd`. Filenames that start with an underscore `_` are skipped. `index.Rmd` will always be treated as the first file.

Alternatively, set the order in `_bookdown.yml`:

```yaml
rmd_files:
  html: ["index.Rmd", "abstract.Rmd", "intro.Rmd"]
  latex: ["abstract.Rmd", "intro.Rmd"]
```



- Benefits
- Quick Start
    - General Usage
        - Front matter
        - Content
    - Write Thesis in English (Write in Eng)
- Bookdown Demo
    - Citation
    - Cross References
    - 數學公式
    - indexing
- Harnessing the Power of R Community
    - Facilitating Packages
        - citr
    - 特定領域
        - linguisticsdown
- Resources
    - R Markdown Features
- Thanks and Help
    - GitHub issues







**You** can label chapter and section titles using `{#label}` after them, e.g., we can reference Chapter \@ref(intro). If you do not manually label them, there will be automatic labels anyway, e.g., Chapter \@ref(methods).



Figures and tables with captions will be placed in `figure` and `table` environments, respectively.

```{r nice-fig, fig.cap='Here is a nice figure!', out.width='80%', fig.asp=.75, fig.align='center'}
par(mar = c(4, 4, .1, .1))
plot(pressure, type = 'b', pch = 19)
```

Reference a figure by its code chunk label with the `fig:` prefix, e.g., see Figure \@ref(fig:nice-fig). Similarly, you can reference tables generated from `knitr::kable()`, e.g., see Table \@ref(tab:nice-tab).

```{r nice-tab, tidy=FALSE}
knitr::kable(
  head(iris, 20), caption = 'Here is a nice table!',
  booktabs = TRUE
)
```

You can write citations, too. For example, we are using the **bookdown** package [@R-bookdown] in this sample book, which was built on top of R Markdown and **knitr**.

