--- 
title: '臺灣大學論文 Bookdown 模板'
author: 'Yongfu Liao'
link-citations: yes
site: bookdown::bookdown_site
geometry: a4paper, left=1.18in, right=1.18in, top=1.18in, bottom=0.787in
fontsize: 12pt
subparagraph: yes
linestretch: 1.5 # If English: 1.5
watermark: false
bibliography: packages.bib
---

# Prerequisites

This is a _sample_ book written in **Markdown** [@R-rmarkdown]. You can use anything that Pandoc's Markdown supports, e.g., a math equation $a^2 + b^2 = c^2$.

The **bookdown** package can be installed from CRAN or Github:

```{r eval=FALSE}
install.packages("bookdown")
# or the development version
# devtools::install_github("rstudio/bookdown")
```

Remember each Rmd file contains one and only one chapter, and a chapter is defined by the first-level heading `#`.

To compile this example to PDF, you need XeLaTeX. You are recommended to install TinyTeX (which includes XeLaTeX): <https://yihui.name/tinytex/>.

```{r include=FALSE}
# automatically create a bib database for R packages
knitr::write_bib(c(
  .packages(), 'bookdown', 'knitr', 'rmarkdown'
), 'packages.bib')
```
