```{r echo=FALSE, include=TRUE}
klippy::klippy(position = c('top', 'right'),
               all_precode = TRUE)
```

# 語法 Cheatsheet {#cheatsheet}

## 數學 {#math}

完整內容，詳見 Bookdown [Ch. 2](https://bookdown.org/yihui/bookdown/markdown-extensions-by-bookdown.html)

### Unnumbered Equations

```latex
\begin{equation*} 
\frac{d}{dx}\left( \int_{a}^{x} f(u)\,du\right)=f(x)
\end{equation*} 
```

\begin{equation*} 
\frac{d}{dx}\left( \int_{a}^{x} f(u)\,du\right)=f(x)
\end{equation*} 


### Numbered Equations
```latex
\begin{equation} 
  f\left(k\right) = \binom{n}{k} p^k\left(1-p\right)^{n-k}
  (\#eq:bino)
\end{equation} 

式 \@ref(eq:bino)
```

\begin{equation} 
  f\left(k\right) = \binom{n}{k} p^k\left(1-p\right)^{n-k}
  (\#eq:binom)
\end{equation} 

式 \@ref(eq:binom)


### Multi-line Aligned Equations

```latex
\begin{equation} 
\begin{split}
\mathrm{Var}(\hat{\beta}) & =\mathrm{Var}((X'X)^{-1}X'y)\\
 & =(X'X)^{-1}X'\mathrm{Var}(y)((X'X)^{-1}X')'\\
 & =(X'X)^{-1}X'\mathrm{Var}(y)X(X'X)^{-1}\\
 & =(X'X)^{-1}X'\sigma^{2}IX(X'X)^{-1}\\
 & =(X'X)^{-1}\sigma^{2}
\end{split}
(\#eq:var-beta)
\end{equation}

詳見公式 \@ref(eq:var-beta)
```

\begin{equation} 
\begin{split}
\mathrm{Var}(\hat{\beta}) & =\mathrm{Var}((X'X)^{-1}X'y)\\
 & =(X'X)^{-1}X'\mathrm{Var}(y)((X'X)^{-1}X')'\\
 & =(X'X)^{-1}X'\mathrm{Var}(y)X(X'X)^{-1}\\
 & =(X'X)^{-1}X'\sigma^{2}IX(X'X)^{-1}\\
 & =(X'X)^{-1}\sigma^{2}
\end{split}
(\#eq:var-bet)
\end{equation} 

詳見公式 \@ref(eq:var-bet)

### 定理與證明 {#theorem-proof}

````markdown
`r ''````{theorem, thm-label, name="Pythagorean theorem"}
For a right triangle, if $c$ denotes the length of the hypotenuse
and $a$ and $b$ denote the lengths of the other two sides, we have

$$a^2 + b^2 = c^2$$
```

詳見定理 \@ref(thm:thm-label)
````

```{theorem, pyth, name="Pythagorean theorem"}
For a right triangle, if $c$ denotes the length of the hypotenuse
and $a$ and $b$ denote the lengths of the other two sides, we have
$$a^2 + b^2 = c^2$$
```

詳見定理 \@ref(thm:pyth)

#### proof, remark, and solution {-}

將 code chunk 中 `theorem` 換成 `proof`, `remark`, `solution`。這三者無法被 cross-reference。見更多[引用環境](https://bookdown.org/yihui/bookdown/markdown-extensions-by-bookdown.html#tab:theorem-envs)。


## Figure Referencing

````markdown
`r ''````{r iris, fig.cap= "The iris data."}
library(ggplot2)
pl_iris <- ggplot(data = iris) +
             geom_point(aes(x = Sepal.Length,
                            y = Sepal.Width,
                            color = Species)
                        )
pl_iris
```
````

```{r iris, fig.cap= "The iris data.", out.width="70%", echo=FALSE}
library(ggplot2)
pl_iris <- ggplot(data = iris) +
             geom_point(aes(x = Sepal.Length,
                            y = Sepal.Width,
                            color = Species)
                        )
pl_iris
```


`見圖 \@ref(fig:iris)`產生：見圖 \@ref(fig:iris)

### Figure Caption

對於比較複雜的 caption，可以使用 Text reference 的方式：

````markdown
對於比較複雜的 caption，可以使用 Text reference 的方式：

(ref:dia) 插入**引用資料** [@kassin2017] 的 Figure Caption.

`r ''````{r dia, fig.cap='(ref:dia)', fig.show='hold', out.width=c('48%','48%')}
ggplot(data = diamonds) +
  geom_point(aes(x = carat, 
                 y = price,
                 color = cut),
             size = 0.1) +
  guides(color = guide_legend(
    override.aes = list(size = 2)
    ))

pl_iris # Second figure
```
````

(ref:foo) 插入**引用資料** [@kassin2017] 的 Figure Caption.

```{r foo, echo=FALSE, fig.cap='(ref:foo)', fig.show='hold', out.width=c('48%','48%')}
ggplot(data = diamonds) +
  geom_point(aes(x = carat, 
                 y = price,
                 color = cut),
             size = 0.1) +
  guides(color = guide_legend(
    override.aes = list(size = 2)
    ))

pl_iris   # Second figure
```


## Table Referencing

```{r include=FALSE}
str <- '`r Sys.time()`'
```

````markdown
(ref:mtcars) Dynamic variable in caption: `r str`.

`r ''````{r mtcars, echo=FALSE}
knitr::kable(
  head(mtcars[, 1:8], 5), booktabs = TRUE,
  caption = '(ref:mtcars)'
  )
```

### Link Table in Later Sections {-}
見表 \@ref(tab:mtcars)
````


(ref:mtcar) Dynamic variable in caption: `r Sys.time()`.

```{r mtcar, echo=FALSE}
knitr::kable(
  head(mtcars[, 1:8], 5), booktabs = TRUE,
  caption = '(ref:mtcar)'
  )
```

### Link Table in Later Sections {-}
見表 \@ref(tab:mtcar)



## 總整理

- `(ref:mtcar) Text refereces`
- `\@ref(fig:fig-label)`
    - `fig-label` is code chunk label
- `\@ref(thm:thm-label)`
    - `thm-label` is code chunk label
- `\@ref(tab:tab-label)`
    - `tab-label` is code chunk label. Use text reference for complicated captions.
- `\@ref(eq:eq-label)`
    - Defined as `(\#eq:eq-label)` in LaTeX equation environment




- Benefits
- Quick Start
    - General Usage
        - Front matter
        - Content
    - Write Thesis in English (Write in Eng)
- Resources
    - R Markdown Features
- Thanks and Help
    - GitHub issues